Visual diagnostics for constrained optimisation with application to guided tours

### 2020-10-17 paper/paper.Rmd
Changes in Section 2.

Given an optimisation problem, two broad approaches find the optimum based on different thinking and hence have its own strength and deficits.
An analytical approach aims to find the optimal solution in a finite number of steps, but the closed-form solution may not be available when the problem starts to become complex. 
An iterative approach, on the other hand, finds the optimum based on the idea of making progressive improvement to the current solution and researchers can decide when to stop if a desirable accuracy has been achieved. However, a potential issue is that it may end up finding a local optimum. In this paper, the main focus is on a particular iterative method:  *line search method* [@fletcher2013practical]. In a simple one-dimensional problem of finding the $x$ that minimises $f(x)$, line search conducts its search via an iterative up as in Equation \ref{eq:line-search}.

\begin{equation}
x^{(j + 1)} = x^{(j)} + \alpha_k* d^{(j)}
\label{eq:line-search}
\end{equation}

where $d^{(j)}$ is the searching direction in iteration $j$, and $\alpha_j$ is the step-size. Theoretical results have demonstrated the global convergence of the algorithm when $\alpha_k$ is chosen by minimising  $f(x^{(j)} + \alpha* d^{(j)})$ [@curry1944method]. However, in practice, this is rarely implemented due to its computational demanding or sometimes the existence of such a minimisation[@fletcher2013practical]. A modified approach is to impose a mandatory decrease in the objective function for each iteration: $f^{(j+1)}> f^{(j)}$ and this approach turns out to be efficient in practical problems despite the lost of guarantee on global convergence.

>>>>

For a given problem we might rely on numeric methods to find the optimal solution, since an analytical approach, requiring a closed-form solution, is often not possible for complex problems.
An iterative approach finds the optimum by progressively improving the current solution. Researchers can then decide when to stop if a desirable accuracy has been achieved. One potential issue with this technique is that it may end up finding a local optimum.

In this paper, the main focus is on the  *line search method* [@fletcher2013practical]. In a simple one-dimensional problem, finding the value of $x$ that minimises the function $f(x)$, the line search takes iterative steps as in Equation \ref{eq:line-search},

\begin{equation}
x^{(j + 1)} = x^{(j)} + \alpha_k* d^{(j)},
\label{eq:line-search}
\end{equation}

where $d^{(j)}$ is the searching direction in iteration $j$, and $\alpha_j$ is the step-size. Theoretical results have demonstrated the global convergence of the algorithm when the step-size $\alpha_k$ is chosen by minimising  $f(x^{(j)} + \alpha* d^{(j)})$ [@curry1944method]. This is however rarely implemented in practice, either because of the high computational demand or because the solution does not exist [@fletcher2013practical]. A modified approach, in the case of maximisation, is to impose a mandatory increase in the objective function for each iteration: $f^{(j+1)}> f^{(j)}$. Similarly, for  minimisation we would require a decrease in function value at each step. This approach turns out to be efficient in practical problems, but global convergence cannot be guaranteed in this case.
